\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.4in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

% Color definitions
\definecolor{primaryColor}{RGB}{15, 23, 42}
\definecolor{linkColor}{RGB}{2, 132, 199}

\hypersetup{
    colorlinks=true,
    linkcolor=primaryColor,
    urlcolor=linkColor
}

\urlstyle{same}

% Section formatting
\titleformat{\section}{\large\bfseries\color{primaryColor}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{4pt}

% Custom itemize settings for tight spacing
\setlist[itemize]{tightlist, leftmargin=12pt, label=$\cdot$}

\begin{document}

\begin{center}
    {\Huge \bfseries \color{primaryColor} Debanjan Biswas} \\ \vspace{3pt}
    {\large Full Stack Engineer \,$\cdot$\, AI-Augmented Developer} \\ \vspace{4pt}
    \small
    \href{mailto:debanjan@partofcosmos.pages.dev}{debanjan@partofcosmos.pages.dev} \,$\cdot$\, 
    \href{https://github.com/partofcosmos-site}{github.com/partofcosmos-site} \,$\cdot$\, 
    \href{https://linkedin.com/in/debanjan-biswas-8200573b8}{linkedin.com/in/debanjan-biswas}
\end{center}

\section{Professional Summary}
Performance-driven Full Stack Developer with 2 years of experience engineering scalable web platforms, custom API infrastructures, and high-velocity automation systems. Specialized in maximizing production output by combining core frontend/backend technologies with state-of-the-art AI tooling, LLM-assisted code orchestration, and agentic workflows. Proven ability to architect real-time data environments, manage technical media pipelines, and continuously deploy robust systems through automated CI/CD protocols.

\section{Technical Skills Matrix}
\begin{itemize}
    \item \textbf{Languages \& Core Runtimes:} C++, C, TypeScript, JavaScript (ES6+), Python, Node.js, HTML5, CSS3, SQL
    \item \textbf{Frameworks \& Web Ecosystem:} Next.js, React.js, Three.js, Express.js, Tailwind CSS, RESTful API Design
    \item \textbf{AI \& Agentic Workflows:} Google Antigravity Agentic IDE, Trae IDE, Google AI Studio API, Prompt Engineering, RAG
    \item \textbf{Database \& Infrastructure:} Supabase, PostgreSQL, MongoDB, Vercel Edge Networks, GitHub Actions
    \item \textbf{Multimedia \& Diagnostics:} Video Pipeline Automation, Sentry Error Monitoring, Android Debug Bridge (ADB)
\end{itemize}

\section{Professional Experience}
\noindent
\textbf{Lead Developer \& Technical Media Strategist} \hfill January 2025 -- Present \\
\textit{Client: Part of Cosmos (Digital Media Brand)} \hfill Remote
\begin{itemize}
    \item \textbf{Architected} and deployed the official client web portal (\href{https://partofcosmos.pages.dev}{partofcosmos.pages.dev}) utilizing Next.js and Vercel edge networks, implementing Three.js for hardware-accelerated 3D client-side rendering.
    \item \textbf{Engineered} a secure, serverless backend utilizing Supabase for real-time relational data management, strict schema validation, and dynamic content delivery.
    \item \textbf{Managed} end-to-end post-production video pipelines for the brand's YouTube distributions, optimizing rendering hardware utilization and applying algorithmic SEO metadata to maximize audience retention.
    \item \textbf{Deployed} complex custom DNS routing rules and automated SSL handshakes to enforce strict security compliance and guarantee maximum platform availability during content drops.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Backend Automation Consultant (Stealth AI Project / NDA)} \hfill May 2024 -- December 2024 \\
\textit{Independent Contract} \hfill Remote
\begin{itemize}
    \item \textbf{Designed} isolated API gateways and secure data pipelines for an undisclosed artificial intelligence toolset, adhering to strict Non-Disclosure Agreement (NDA) confidentiality requirements.
    \item \textbf{Accelerated} software lifecycles by integrating Google Antigravity Agentic IDE and Trae IDE to automate boilerplate generation and orchestrate complex local build systems.
    \item \textbf{Constructed} automated testing environments for local LLM integrations, sanitizing data inputs and optimizing context window parsing for raw C++ and Python data streams.
    \item \textbf{Maintained} zero-downtime microservices during the rapid prototyping phase, utilizing serverless edge functions to handle erratic, unpredicted traffic spikes.
\end{itemize}

\section{Research \& Academic Initiatives}
\noindent
\textbf{IIT Kharagpur RISE / I-KITES} \hfill June 16, 2026 -- Present \\
\textit{Research Scholar / Participant} \hfill Kharagpur, India
\begin{itemize}
    \item \textbf{Participating} in the prestigious research, innovation, and entrepreneurship training program hosted by IIT Kharagpur, focusing on technical systems and scientific modeling.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{NSRI Research Community} \hfill 2026 -- Present \\
\textit{Research Member} \hfill Remote
\begin{itemize}
    \item \textbf{Collaborating} on open-source scientific codebases, decentralized developer environments, and physics computations.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Synthica Research Community} \hfill 2026 -- Present \\
\textit{Research Member} \hfill Remote
\begin{itemize}
    \item \textbf{Contributing} to machine learning pipelines, automated code validation systems, and agentic workflows.
\end{itemize}

\section{Community \& Open Source}
\noindent
\textbf{Hack Club Global Developer Network} \,$\cdot$\, \textit{Community Member} \hfill December 2025 -- Present
\begin{itemize}
    \item Engaged in peer-led open-source software development, actively collaborating on decentralized environments, deployment architectures, and technical hackathons.
\end{itemize}

\end{document}
